Multiple Linear Regression on Sleep Data

### 2025-05-08 paper/paper.qmd
fix
formatting
cross validation

\noindent\textbf{\Large Motivation}

@@

\noindent\textbf{\Large About the Data}

@@

\noindent\textbf{\Large Exploratory Data Analysis}

@@

\noindent\textbf{\Large Full Model}

@@

\noindent\textbf{\Large Updated Model}

@@

For our suggested regression, we used LASSO regression. We hoped to extract the most import input features to achieve a simple yet powerful model. To find the optimal $\lambda$ or the regularization parameter, we used a cross-validation process by splitting our data set: train = 80%. We saw that `gender`, `occupation`, `bmi_category`, and `sleep_disorder` converged to zero.

@@

```{r}
kable(nonzero_coefs_df, digits = 4, caption = "Non-Zero Coefficients from LASSO (Selected by Cross-Validation)",
      row.names = FALSE)
```

@@

final_model <- lm(sleep_duration ~., sleep_test_final)
final_model_summary <- summary(model_final)

@@

>>>>

\begin{center}
\Large\textbf{\large Introduction}
\end{center}

\noindent\textbf{Motivation}

@@

\noindent\textbf{About the Data}

@@

\noindent\textbf{Exploratory Data Analysis}

@@

\begin{center}
\Large\textbf{\large Finding Our Model}
\end{center}

\noindent\textbf{Full Model}

@@

\noindent\textbf{Updating Model: VIF and Lasso Considerations}

@@

For our suggested regression, we used LASSO regression. We hoped to extract the most import input features to achieve a simple yet powerful model. To find the optimal $\lambda$ or the regularization parameter, we used a cross-validation process by splitting our data set: train = 80%. We saw that `gender`, `occupation`, `bmi_category`, and `sleep_disorder` converged to zero. Optimal lambda value was 0.0009622.

@@

```{r}
kable(nonzero_coefs_df, digits = 4, caption = "Non-Zero Coefficients from LASSO (Selected by Cross-Validation)",
      row.names = FALSE)

# Create a tibble with the optimal lambda
lambda_table <- tibble(
  Description = "Optimal lambda (lambda.min)",
  Value = cvmodelL$lambda.min
)

# Display in kable format
kable(lambda_table, caption = "Optimal Lambda from Cross-Validation")

@@

final_model <- lm(sleep_duration ~., sleep_test_final)
final_model_summary <- summary(final_model)

@@

\begin{center}
\Large\textbf{\large Discussion}
\end{center}

```{r include=FALSE}
library(caret)
library(knitr)
library(dplyr)

set.seed(510)

# Set up 10-fold cross-validation
train_control <- trainControl(method = "cv", number = 10)

# 1. Initial model using full dataset
cv_full <- train(sleep_duration ~ ., data = sleep, method = "lm", trControl = train_control)

# 2. Final model using sleep_test_final dataset
cv_final <- train(sleep_duration ~ ., data = sleep_test_final, method = "lm", trControl = train_control)

# 3. Extract RMSE and R-squared
cv_results <- tibble(
  Model = c("Initial Model", "Final Model"),
  RMSE = c(cv_full$results$RMSE, cv_final$results$RMSE),
  Rsquared = c(cv_full$results$Rsquared, cv_final$results$Rsquared)
)

```{r}
# 4. Display as kable table
kable(cv_results, caption = "10-Fold Cross-Validation Results for Initial and Final Models")
```
